Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex

\section{Design}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
  \vspace{-26 pt}
  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data. Right: The game interface.}
  \label{fig:user}
\end{figure*}

@@

We will first describe the flow a typical user would take when using this application. The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see after the child has played the game.

\subsubsection{Game (Kimbee)}

[User Flow Game Here]

\subsubsection{Therapist Portal}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \caption{\normalfont Left: The Therapist Portal, the user system of the therapist. Middle: The Central Server, hosts the recordings and facilitates interactions. Right: The Kimbee Game, interactive game that allows practice of speech for children. }
  \label{fig:tech}
\end{figure*}

>>>>

\section{Application Design}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
  \vspace{-22 pt}
  \caption{\normalfont Left: The game, {\em Kimbee}, where children play the role of a bee trying to collect honey as a resource. Right: The flow diagram showing how therapists and children exchange data through the game and the portal.}
  \label{fig:user}
\end{figure*}

@@

The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see after the child has played the game. This will follow the example that the therapist has assigned {\em Kimbee} as homework for the child to do at home outside of the session. When the game is launched for the first time, a unique identification string is generated as a token for the child. This token should then be sent to the therapist allowing them to track the progress of the student. It is suggested that this first launch and setup take place in an in-person session with the therapist to alleviate any technical problems that may arise.

\subsubsection{Gameplay}

The game has a simple interface that is easy for a child to navigate, see Figure \ref{fig:user}. Children simply tap the screen to make their character, a bee, move along the y-axis of the screen. Collecting honey causes their score to increase and colliding with an enemy bee causes the game to end. Interleaved with the enemy bees and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed. This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen. The difficulty of the text increases over time to simulate the treatment that the child would receive during a therapist session \cite{Rosenbek:Treatment}. If the system succeeds in verifying that the child spoke the text correctly, then the currency is added to the child's score. If the child fails to correctly pronounce the phrase or if the system fails to recognize the audio, then the child is asked to try again in order to continue. To avoid discouraging the child, {\em Kimbee} will say a positive statement asking him or her to try again to continue playing the game \cite{Kreider:Intro}.

After every challenge, the audio spoken by the child is encoded and sent to the central data server, see Figure \ref{fig:user} for a diagram of this. These data can be examined and reviewed in the therapist portal.

\subsubsection{Therapist Review}

@@

\subsection{Currency}

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \vspace{-23 pt}
  \caption{\normalfont Left: The Therapist Portal, the user system of the therapist. Middle: The Central Server, hosts the recordings and facilitates interactions. Right: The Kimbee Game, interactive game that allows practice of speech for children. }
  \label{fig:tech}
\end{figure*}
